Nonparametric Goodness-of-Fit Tests \\ for Discrete Null Distributions

### 2010-10-14 JSS/article.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/ks-test@18 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

>>>>

\begin{Schunk}
\begin{Sinput}
set.seed(1)
REPS <- 100000
asymp.pval <- rep(0, REPS)
exact.pval <- rep(0, REPS)
for (i in 1:REPS) {
  x <- sample(1:10, 15, replace=TRUE)
  asymp.pval[i] <- stats::ks.test(x, ecdf(1:10), alternative="g")$p.value
  exact.pval[i] <- ks.test::ks.test(x, ecdf(1:10), alternative="g")$p.value
}
sum(asymp.pval<exact.pval)/REPS
sum(asymp.pval<=0.05)/REPS
sum(exact.pval<=0.05)/REPS
sqrt(0.05*0.95/REPS)
\end{Sinput}
\end{Schunk}

\begin{verbatim}
#####################################################
# 100000:

> sum(asymp.pval<exact.pval)/REPS
[1] 0
> sum(asymp.pval<=0.05)/REPS
[1] 0.01848
> sum(exact.pval<=0.05)/REPS
[1] 0.03763
> 
> sqrt(0.05*0.95/REPS)
[1] 0.0006892024
> 
> REPS
[1] 1e+05
\end{verbatim}
